---
title: "Homework 8"
author: "Maddie Winer"
date: "2025-03-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
**Question 1**
-
*Copy and paste the code below into different code chunks, and then read the text and run the code chunks one at a time to see what they do. *

```{r}
#open libraries
library(ggplot2) 
library(MASS) 

#read in data vector
z <- rnorm(n=3000,mean=0.2)
z <- data.frame(1:3000,z)
names(z) <- list("ID","myVar")
z <- z[z$myVar>0,]
str(z)
summary(z$myVar)

#plot histogram 
p1 <- ggplot(data=z, aes(x=myVar, y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",linewidth=0.2) 
print(p1)

#add empirical density curve 
p1 <-  p1 +  geom_density(linetype="dotted",size=0.75)
print(p1)

#get maximum likelihood parameters for normal
normPars <- fitdistr(z$myVar,"normal")
print(normPars)
str(normPars)
normPars$estimate["mean"] 

#plot normal probability density
meanML <- normPars$estimate["mean"]
sdML <- normPars$estimate["sd"]

xval <- seq(0,max(z$myVar),len=length(z$myVar))

 stat <- stat_function(aes(x = xval, y = ..y..), fun = dnorm, colour="red", n = length(z$myVar), args = list(mean = meanML, sd = sdML))
 p1 + stat

#plot exponential probability density
expoPars <- fitdistr(z$myVar,"exponential")
rateML <- expoPars$estimate["rate"]

stat2 <- stat_function(aes(x = xval, y = ..y..), fun = dexp, colour="blue", n = length(z$myVar), args = list(rate=rateML))
 p1 + stat + stat2
 
#plot uniform probability density
stat3 <- stat_function(aes(x = xval, y = ..y..), fun = dunif, colour="darkgreen", n = length(z$myVar), args = list(min=min(z$myVar), max=max(z$myVar)))
 p1 + stat + stat2 + stat3
 
#plot gamma probability density
gammaPars <- fitdistr(z$myVar,"gamma")
shapeML <- gammaPars$estimate["shape"]
rateML <- gammaPars$estimate["rate"]

stat4 <- stat_function(aes(x = xval, y = ..y..), fun = dgamma, colour="brown", n = length(z$myVar), args = list(shape=shapeML, rate=rateML))
 p1 + stat + stat2 + stat3 + stat4
 
#plot beta probability density
pSpecial <- ggplot(data=z, aes(x=myVar/(max(myVar + 0.1)), y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) + 
  xlim(c(0,1)) +
  geom_density(size=0.75,linetype="dotted")

betaPars <- fitdistr(x=z$myVar/max(z$myVar + 0.1),start=list(shape1=1,shape2=2),"beta")
shape1ML <- betaPars$estimate["shape1"]
shape2ML <- betaPars$estimate["shape2"]

statSpecial <- stat_function(aes(x = xval, y = ..y..), fun = dbeta, colour="orchid", n = length(z$myVar), args = list(shape1=shape1ML,shape2=shape2ML))
pSpecial + statSpecial
 
```

**Question 2**
-
*Try it with your own data (starwars). Once the code is in and runs, try running this analysis on your own data.*

```{r}
#prepare our data
library(tidyverse)
z0 <- data.frame(starwars)
z <- na.omit(z0)
#view(z)
str(z)
summary(z)

#plot histogram
p1 <- ggplot(data=z, aes(x=height, y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",linewidth=0.2) 
print(p1)

#add empirical density curve 
p1 <-  p1 +  geom_density(linetype="dotted",size=0.75)
print(p1)

#get maximum likelihood parameters for normal
normPars <- fitdistr(z$height,"normal")
print(normPars)
str(normPars)
normPars$estimate["mean"] 

#plot normal probability density
meanML <- normPars$estimate["mean"]
sdML <- normPars$estimate["sd"]

xval <- seq(0,max(z$height),len=length(z$height))

 stat <- stat_function(aes(x = xval, y = ..y..), fun = dnorm, colour="red", n = length(z$height), args = list(mean = meanML, sd = sdML))
 p1 + stat

#plot exponential probability density
expoPars <- fitdistr(z$height,"exponential")
rateML <- expoPars$estimate["rate"]

stat2 <- stat_function(aes(x = xval, y = ..y..), fun = dexp, colour="blue", n = length(z$height), args = list(rate=rateML))
 p1 + stat + stat2
 
#plot uniform probability density
stat3 <- stat_function(aes(x = xval, y = ..y..), fun = dunif, colour="darkgreen", n = length(z$height), args = list(min=min(z$height), max=max(z$height)))
 p1 + stat + stat2 + stat3
 
#plot gamma probability density
gammaPars <- fitdistr(z$height,"gamma")
shapeML <- gammaPars$estimate["shape"]
rateML <- gammaPars$estimate["rate"]

stat4 <- stat_function(aes(x = xval, y = ..y..), fun = dgamma, colour="brown", n = length(z$height), args = list(shape=shapeML, rate=rateML))
 p1 + stat + stat2 + stat3 + stat4
 
#plot beta probability density
pSpecial <- ggplot(data=z, aes(x=height/(max(height + 0.1)))) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) + 
  xlim(c(0,1)) +
  geom_density(size=0.75,linetype="dotted")

betaPars <- fitdistr(x=z$height/max(z$height + 0.1),start=list(shape1=1,shape2=2),"beta")
shape1ML <- betaPars$estimate["shape1"]
shape2ML <- betaPars$estimate["shape2"]

statSpecial <- stat_function(aes(x = xval, y = ..y..), fun = dbeta, colour="orchid", n = length(z$height), args = list(shape1=shape1ML,shape2=shape2ML))
pSpecial + statSpecial

```

**Question 3**
-
*Identify which distribution curve best fits the data.*
<br>
<br>
Normal Probability Density curve best fits the data without including bias like the beta density curve.


**Question 4**
- 
*Simulate a new data set.*
<br>
<br>
No, the model is not doing a good job because we used "rnorm" to generate a new dataset that does not match the same distribution of data from the original. Additionally, the sample size is small and might not be able to show the best density distribution curve for the original data to be used for the simulated data. 
```{r}
###Simulated Data
library(ggplot2) 
library(MASS)
d <- rnorm(n=29,mean=178.66)
d <- data.frame(1:29,d)
names(d) <- list("ID","height")
d <- d[d$height>0,]
str(d)
summary(d$height)

#plot histogram
p1 <- ggplot(data=d, aes(x=height, y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",linewidth=0.2) 
print(p1)

#add empirical density curve 
p1 <-  p1 +  geom_density(linetype="dotted",size=0.75)
print(p1)

###Original Data
library(tidyverse)
z0 <- data.frame(starwars)
z <- na.omit(z0)
#view(z)
str(z)
summary(z)

#plot histogram
p1 <- ggplot(data=z, aes(x=height, y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",linewidth=0.2) 
print(p1)

#add empirical density curve 
p1 <-  p1 +  geom_density(linetype="dotted",size=0.75)
print(p1)
```



