---
title: "Homework 6"
author: "Maddie Winer"
date: "2025-02-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
**Write code to create a random data set with a normal distribution and defined standard deviation, sample size, and mean.**
-
```{r}
response_1 <- rnorm(n=100, mean=15, sd=2)
print(response_1)
response_2 <- rnorm(n=100, mean=30, sd=7)
print(response_2)
response <- c(response_1, response_2)
```

**Organize these data into a data frame with the appropriate structure.**
-
```{r}
my_df_1 <- data.frame (X = "control", Y= response_1)
print(my_df_1)
my_df_2 <- data.frame(X = "treatment", Y = response_2)
print(my_df_2)
my_df <- rbind(my_df_1, my_df_2)
print(my_df)
```

**Analyze and graph the data.**
-
```{r}
anova_data <- aov(Y ~ X, data = my_df)
summary <- summary(anova_data)
print(summary[[1]]$`Pr(>F)`)
library(ggplot2)
plot <- ggplot(my_df, aes(X, Y)) + geom_boxplot() + labs(x="Conditions",y="Responses")
print(plot)
```

**For Loop Generation- ADJUSTING SAMPLE SIZE**
-
```{r}
n <- seq(50, 300, 10)
for (i in 1:length(n)) {
  print(n[i])
}

response_1 <- rnorm(n=n[i], mean=15, sd=2)
print(response_1)
response_2 <- rnorm(n=n[i], mean=30, sd=7)
print(response_2)
response <- c(response_1, response_2)

my_df_1 <- data.frame (X = "control", Y= response_1)
print(my_df_1)
my_df_2 <- data.frame(X = "treatment", Y = response_2)
print(my_df_2)
my_df <- rbind(my_df_1, my_df_2)
print(my_df)

anova_data <- aov(Y ~ X, data = my_df)
summary_sample <- summary(anova_data)
print(summary_sample[[1]]$`Pr(>F)`)
library(ggplot2)
plot <- ggplot(my_df, aes(X, Y)) + geom_boxplot() + labs(x="Conditions",y="Responses")
print(plot)
```
**For Loop Generation- ADJUSTING MEAN**
-
```{r}
n <- sample(1:30)
for (i in 1:length(n)) {
  print(n[i])
}

response_1 <- rnorm(n=100, mean=n[i], sd=2)
print(response_1)
response_2 <- rnorm(n=100, mean=n[i], sd=7)
print(response_2)
response <- c(response_1, response_2)

my_df_1 <- data.frame (X = "control", Y= response_1)
print(my_df_1)
my_df_2 <- data.frame(X = "treatment", Y = response_2)
print(my_df_2)
my_df <- rbind(my_df_1, my_df_2)
print(my_df)

anova_data <- aov(Y ~ X, data = my_df)
summary_mean <- summary(anova_data)
print(summary_mean[[1]]$`Pr(>F)`)
library(ggplot2)
plot <- ggplot(my_df, aes(X, Y)) + geom_boxplot() + labs(x="Conditions",y="Responses")
print(plot)

```


**For Loop Generation- ADJUSTING SD**
-
```{r}
n <- sample(1:20)
for (i in 1:length(n)) {
  print(n[i])
}

response_1 <- rnorm(n=100, mean=15, sd=n[i])
print(response_1)
response_2 <- rnorm(n=100, mean=30, sd=n[i])
print(response_2)
response <- c(response_1, response_2)

my_df_1 <- data.frame (X = "control", Y= response_1)
print(my_df_1)
my_df_2 <- data.frame(X = "treatment", Y = response_2)
print(my_df_2)
my_df <- rbind(my_df_1, my_df_2)
print(my_df)

anova_data <- aov(Y ~ X, data = my_df)
summary_sd <- summary(anova_data)
print(summary_sd[[1]]$`Pr(>F)`)
library(ggplot2)
plot <- ggplot(my_df, aes(X, Y)) + geom_boxplot() + labs(x="Conditions",y="Responses")
print(plot)
```

**Comparing p-values**
-
```{r}
print(summary[[1]]$`Pr(>F)`)
print(summary_sample[[1]]$`Pr(>F)`)
print(summary_mean[[1]]$`Pr(>F)`)
print(summary_sd[[1]]$`Pr(>F)`)

```
**Discussion on p-values**
-
(1) When changing the sample size, the p-value became more significant.
(2) When changing the mean, the p-value became insignificant. 
(3) When changing the standard deviation, the p-value became more significant. 


