---
title: "Homework 10"
author: "Maddie Winer"
date: "2025-04-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
**Create FOUR visualizations using ggplot**  
Download libraries and packages for data.
```{r}
library(ggplot2)
library(waffle)
library(ggthemes)
library(tidytuesdayR)
library("wesanderson")
library(pals)
library(scatterpie)
library(beeswarm)

tuesdata <- tidytuesdayR::tt_load('2022-02-01')
#tuesdata <- tidytuesdayR::tt_load(2022, week = 5)

breed_traits <- tuesdata$breed_traits
```


**Graph 1**
-
Waffle plot to look at range of subplots at site.
```{r}
tabled_data <- as.data.frame(table(coat_type=breed_traits$`Coat Type`))

waffle <- ggplot(data=tabled_data) +
  aes(fill = coat_type, values = Freq) +
  waffle::geom_waffle(n_rows = 10, size = 0.33, colour = "black") + 
  coord_equal() +
  theme_void() 
  #scale_fill_manual(values=c("coral","grey95","goldenrod","red","green","blue","yellow","brown","orange","grey"))
waffle 

```

**Graph 2**
-
Ridgeline plot compare coat type with how well the breed 
```{r}
d <- data.frame(Breed=breed_traits$Breed ,With_Children=breed_traits$`Good With Young Children`, Other_Dogs = breed_traits$`Good With Other Dogs`, Coat_Type=breed_traits$`Coat Type`, Bark_Rating = breed_traits$`Barking Level`)
ridgeline <- ggplot(data=d) +
  aes(x=With_Children,y=Coat_Type,fill=Coat_Type) + 
  ggridges::geom_density_ridges() +
  ggridges::theme_ridges() 
ridgeline  

```

**Graph 3**
-
Beeswarm plot to compare coat type with friendliness with other dogs. Each dot represents one breed. 
```{r}
beeswarm <- ggplot(data=d) +
  aes(x=Coat_Type,y=Other_Dogs,color=Coat_Type) + 
  ggbeeswarm::geom_beeswarm(method = "center",size=2) 
beeswarm
```

**Graph 4**
-
Lollipop plot to look at hairless breeds and their ratings for barking level. 
```{r}
d <- data.frame(Breed=breed_traits$Breed,Coat_Type=breed_traits$`Coat Type`, Bark_Rating = breed_traits$`Barking Level`)

edit_d<-d[d$Coat_Type=="Hairless",]

Lollipop <- ggplot(data=edit_d) +
  aes(x=Breed, y= Bark_Rating) +
  geom_segment(aes(x=Breed, 
                   xend=Breed, y=0, 
                   yend=Bark_Rating), 
               color="grey",
               linewidth=2) +
  geom_point( color="orange", size=7) +
  labs(title="Hairless Breeds and their Bark Rating",
       x="",
       y="Bark Rating") +
  coord_flip() +
  theme_light(base_size=20,base_family=
                "Monaco") +
  theme(
    panel.grid.major.x = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    plot.title.position = "plot",  
    plot.title = element_text(hjust = 0))  
Lollipop
```


